%%%%%%%%%%%%%%%%%%%%%%%%
%
% $Author: Sadegh Naderi $
% $Datum: 2023-05-02  $
% $Pfad: BA23-02-Sales-Predictor/report/Contents/en/Packages.tex $
% $Version: 1.0 $
% $Reviewed by: Deepti, Sadegh and Raunak $
% $Review Date: 2023-05-05 $
%
%%%%%%%%%%%%%%%%%%%%%%%%

\chapter{Libraries, Packages and Frameworks}

\section{Introduction}

Data science has become an integral part of various industries, ranging from finance to healthcare, and has revolutionized the way businesses operate. In recent years, there has been an explosion in the amount of data generated, leading to a growing need for tools that can handle large and complex datasets efficiently. This has led to the development of a wide range of data science packages that provide functionality for data manipulation, visualization, and machine learning.
These data science packages are essential tools for any data scientist, as they provide the necessary functionality to efficiently analyze and manipulate data, build powerful models, and gain insights from complex datasets. The packages discussed in this report - pandas, numpy, matplotlib, datetime, seaborn, sklearn, xgboost, keras, lightgbm, and tensorflow - are among the most popular and widely used data science packages. They are open-source, easy to use, and provide extensive documentation, making them accessible to both novice and experienced data scientists.

\section{Pandas}

The term "pandas" is derived from "panel data", which is an econometrics term used for datasets that consist of observations over multiple time periods for the same individuals. [\cite{Mckinney:2011}] The name "pandas" is a clever play on words, combining the words "Python data analysis" with the econometrics term. [\cite{Mckinney:2022}] Pandas is a data manipulation package that allows for the analysis of tabular data. It provides functionality for cleaning, merging, and transforming data. Pandas is built on top of the numpy package and allows for the easy manipulation of dataframes and series.

\section{Numpy}

NumPy is a powerful Python package that serves as the foundation for scientific computing and data analysis. It provides a multidimensional array object, along with a comprehensive set of functions and tools for working with arrays. NumPy's array structure allows for efficient storage and manipulation of large datasets, enabling fast numerical computations and mathematical operations. Its vast collection of mathematical functions, including linear algebra, Fourier transforms, and random number generation, makes it an indispensable tool for scientific and data-intensive applications. NumPy's simplicity, performance, and integration with other scientific libraries have made it the go-to choice for professionals and researchers in fields such as physics, engineering, finance, and machine learning.

\section{Matplotlib}

Matplotlib is a comprehensive Python package that facilitates 2D plotting and generates high-quality graphs suitable for use in professional settings. It supports both interactive and non-interactive plotting and can save output images in multiple formats such as PNG. Additionally, it offers an array of plot types, including lines, bars, pie charts, and histograms, among others. Matplotlib is highly customizable, flexible, and user-friendly. [\cite{Tosi:2009}]

\section{Datetime}

Datetime is a package that provides functionality for working with dates and times. It allows for the easy manipulation of dates and times, including arithmetic operations and formatting. Datetime is often used in conjunction with pandas to manipulate date and time data.

\section{Seaborn}

Seaborn is a Python data visualization library that is built on top of the popular visualization library Matplotlib. It provides a high-level interface for creating informative and attractive statistical graphics. Seaborn comes with several built-in themes and color palettes to make it easy to create aesthetically pleasing visualizations. These plots are optimized for visualizing statistical relationships in data and are often used for exploratory data analysis, data preprocessing, and communicating the results of statistical analyses.

\section{Sklearn}

Scikit-learn, also known as sklearn, is a widely used Python package for machine learning. It is an open-source library that provides a range of tools and algorithms for data analysis, data preprocessing, feature extraction, and model selection. Scikit-learn is built on top of NumPy, SciPy, and matplotlib, and is designed to be user-friendly and efficient. It includes a variety of machine learning algorithms such as regression, classification, clustering, and dimensionality reduction, as well as tools for model evaluation and selection. Scikit-learn is widely used in academia and industry and is considered one of the most popular and powerful machine learning packages available for Python.

\section{Xgboost}

Xgboost (short for "extreme gradient boosting") is a popular open-source machine learning package that is used for building and optimizing high-performance models for classification and regression problems. It is an implementation of the gradient boosting decision tree algorithm, which combines the predictions of several decision trees to produce a final output.

Xgboost is known for its speed, accuracy, and efficiency, and has been widely adopted in various industries for solving complex problems such as predicting customer churn, fraud detection, and image classification. It supports both CPU and GPU training and provides several optimization techniques, such as regularized learning and early stopping, to improve the accuracy of the models. Additionally, it has a user-friendly interface and is compatible with other popular machine learning packages like scikit-learn and pandas. Tianqi Chen and Carlos Guestrin have developed a highly efficient and scalable implementation of XGBoost. [\cite{Chen:2016}]

\section{Keras}


Keras is a user-friendly, high-level Python library for deep learning that can be integrated with TensorFlow, Theano, or CNTK. It allows developers to focus on the essential aspects of deep learning, such as designing neural network layers, without worrying about the complex mathematical details of tensors and their shapes. TensorFlow, Theano, or CNTK must be used as the back-end for Keras. With Keras, users can develop deep learning applications without directly interacting with the intricacies of the underlying framework.
Keras offers two primary APIs: the sequential API and the functional API. The sequential API is based on the concept of a sequence of layers, making it the most common and straightforward use of Keras. The sequential model is a linear stack of layers, where each layer is added in sequence, allowing for easy construction of a neural network model. [\cite{Manaswi:2018}]

\section{Lightgbm}

It is mentioned that in terms of processing speed and model accuracy when dealing with varying numbers of features and records, LightGBM outperforms both CatBoost and XGBoost. [\cite{Al:2019}]
The Python packages discussed here are some of the most powerful and widely used tools in data science and machine learning. Pandas and NumPy provide essential data manipulation and array computation functions, while Matplotlib and Seaborn allow for the creation of high-quality visualizations. The machine learning libraries, including Scikit-learn, XGBoost, Keras, TensorFlow, and LightGBM, enable developers to build and optimize complex models with ease. Each of these packages has its unique strengths and features that make them suitable for various data analysis and modeling tasks. 


